\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Joseph Norkplim Attah} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+233(050) 476-1981 \\ Kumasi, Ghana} 
\address{\href{mailto:josephattah005@gmail.com}{josephattah005@gmail.com} \\ \href{https://linkedin.com/in/joseph-attah-norkplim}{linkedin.com/in/joseph} \\ \href{https://github.com/Joe-Degs}{github.com/Joe-Degs}}

\begin{document}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BSc in Human Settlement Planning}, Kwame Nkrumah University of Science and Technology \hfill {October 2022}\\
CWA: 63.90
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, Go, Javascript, Bash, C, SQL \\
Tools & Git, Docker, Kubernetes, GCP, Qemu, VirtualBox, Terraform, Vagrant, Linux, PostgreSQL, \\
&       QGIS \\
\\
Technical Skills & Systems and Network Programming, IP Networking, Virtualization, Automation, Documentation \\
Soft Skills & Time Management, Teamwork, Communication, Problem Solving, Leadership, Accountability
\\
\end{tabular}\\
\end{rSection}



%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{net} \textbf{|} {Python, Bash, Socket Programming, Network Programming} \hfill \href{https://github.com/Joe-Degs/net}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a Python module that abstracts away the socket layer making tcp, udp and unix socket programming easier.
    \item Wrote a detailed technical documentation in Markdown and Bash automation scripts for testing on linux.
    \item Utilized Go net package's implementation as a guide increasing my understanding of Go's networking package, socket programming and IP networking significantly.
 \end{itemize}

\item \textbf{emulator} \textbf{|} {Go, C, RISC-V, GCC, VirtualBox, Linux Kernel, Qemu} \hfill \href{https://github.com/Joe-Degs/emulator}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a RISC-V emulator capable of interpreting and executing the "rv64i" subset of the ISA.
    \item Implemented the complete "rv64i" subset of RISC-V specification with a functional virtual memory model and memory mapping unit capable of mapping elf binaries into virtual memory and executing them.
    \item Utilized opensource technical documents from riscv.org as guide increasing my understanding of CPU's and their instruction set architectures.
    \item Learned a great deal about compilers, cross compiling and how to build cross compilers, compiling for the first time a 2.5mb linux kernel and running it in Qemu.
 \end{itemize}

\item \textbf{autogis} \textbf{|} {Python, osmnx, networkx, OSM, QGIS, Urban Informatics} \hfill \href{https://github.com/Joe-Degs/AutoGIS/tree/master/test-thesis/autogis}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a tool for visualizing and analysing street networks.
     \item Implemented functionality to (reverse) geocode addresses, geographic coordinates and place names, plot street networks and compute and visualize shortest path between two places.
    \item Utilized opensource tools, data and documentation which improved my understanding of urban informatics and opensource mapping significantly.
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Volunteer IT Support Personnel - Prempeh II Library ICT Center, KNUST.
\end{itemize}


\end{rSection}

%------------------------
% Use this more detailed section if you have Relevant work experience
% keep your resume to 1 page, if you need to remove a project to display relevant experience
% that is okay
% ----------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Software Developer Intern} \hfill December 2021 - February 2022\\
KoldChain \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Wrote tests for Django models improving test coverage in the service by 70\%.
     \item Worked in a team environment improving planning, time management and communication skills significantly.
 \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

\end{rSection} 

% \begin{rSection}{Work History}
% \vspace{-1.25em}
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \end{rSection} 

%----------------------------------------------------------------------------------------

\end{document}
